Distributions

### 2022-01-06 Ch2_distributions/Ch2_Figures.Rmd
Minor details to the figure.

cp.best

pp.boot.fits %>%
  filter(., dBIC == 0) %>% 
  dplyr::select(group, boot, estimate, param, dist) %>% 
  pivot_wider(names_from = param, values_from = estimate) -> pp.best

np.boot.fits %>%
  filter(., dBIC == 0) %>% 
  dplyr::select(individual, boot, estimate, param, dist) %>% 
  pivot_wider(names_from = param, values_from = estimate) %>% 
  mutate(id = str_remove(individual, "B"), 
         group = case_when(
    id %in% c(1,3,5) ~ "G1",
    id %in% c(7) ~ "G2",
    id %in% c(13, 19) ~ "G3",
    id %in% c(22) ~ "G4",
    id %in% c(28) ~ "G5",
    id %in% c(49, 84) ~ "G6",
    id %in% c(29, 30) ~ "G7"
  )) %>%
  #slice_sample(., n = 100) %>% 
  arrange(group) %>% 
  group_by(group) %>% 
  mutate(shapeid = as.character(as.numeric(as.factor(individual)))) -> np.best
#View(np.best)

@@

cp.best %>% 
  filter(., dist == "lnorm") %>% 
  ggplot(., aes(x = meanlog, y = sdlog)) +
  geom_point(alpha = aval) +
  lims(x = c(0.7, 3.5), y = c(0.5, 2.1)) +
  figx.theme -> cp.ln

@@

cp.grid <- plot_grid(NULL, cp.ln, cp.wei, ncol = 3)

pp.best %>% 
  filter(., dist == "gamma") %>% 
  ggplot(., aes(x = rate, y = shape, color = group)) +
  geom_point(alpha = aval) +
  scale_color_manual(values=colsx) +
  lims(x = c(0, 0.23), y = c(0.4, 2.3)) +
  figx.theme -> pp.gam

pp.best %>%
  filter(., dist == "lnorm") %>% 
  ggplot(., aes(x = meanlog, y = sdlog, color = group)) +
  geom_point(alpha = aval) +
  scale_color_manual(values=colsx) +
  lims(x = c(0.7, 3.5), y = c(0.5, 2.1)) +
  figx.theme -> pp.ln

pp.best %>%
  filter(., dist == "weibull") %>% 
  ggplot(., aes(x = scale, y = shape, color = group)) +
  geom_point(alpha = aval) +
  scale_color_manual(values=colsx) +
  lims(x = c(5, 80), y = c(0, 2.1)) +
  figx.theme -> pp.wei

@@

np.best %>% 
  filter(., dist == "gamma") %>% 
  ggplot(., aes(x = rate, y = shape, color = group, shape = shapeid)) +
  geom_point(alpha = aval) +
  scale_color_manual(values=colsx) +
  lims(x = c(0, 0.23), y = c(0.4, 2.3)) +
  figx.theme -> np.gam

np.best %>% 
  filter(., dist == "lnorm") %>% 
  ggplot(., aes(x = meanlog, y = sdlog, color = group, shape = shapeid)) +
  geom_point(alpha = aval) +
  scale_color_manual(values=colsx) +
  lims(x = c(0.7, 3.5), y = c(0.5, 2.1)) +
  figx.theme -> np.ln

np.best %>%
  filter(., dist == "weibull") %>% 
  ggplot(., aes(x = scale, y = shape, color = group, shape = shapeid)) +
  geom_point(alpha = aval) +
  scale_color_manual(values=colsx) +
  lims(x = c(5, 80), y = c(0, 2.1)) +
  figx.theme -> np.wei

@@

>>>>

pp.boot.fits %>%
  filter(., dBIC == 0) %>% 
  dplyr::select(group, boot, estimate, param, dist) %>% 
  pivot_wider(names_from = param, values_from = estimate) %>% 
  mutate(group = as.factor(group)) -> pp.best

np.boot.fits %>%
  filter(., dBIC == 0) %>% 
  dplyr::select(individual, boot, estimate, param, dist) %>% 
  pivot_wider(names_from = param, values_from = estimate) %>% 
  mutate(id = str_remove(individual, "B"), 
         group = case_when(
    id %in% c(1,3,5) ~ "G1",
    id %in% c(7) ~ "G2",
    id %in% c(13, 19) ~ "G3",
    id %in% c(22) ~ "G4",
    id %in% c(28) ~ "G5",
    id %in% c(49, 84) ~ "G6",
    id %in% c(29, 30) ~ "G7"
  )) %>%
  #slice_sample(., n = 100) %>%
  mutate(group = as.factor(group)) %>% 
  arrange(group) %>% 
  group_by(group) %>% 
  mutate(shapeid = as.character(as.numeric(as.factor(individual)))) -> np.best
#View(np.best)

@@

cp.best %>% 
  filter(., dist == "lnorm") %>% 
  ggplot(., aes(x = meanlog, y = sdlog)) +
  geom_point(alpha = aval) +
  lims(x = c(0.7, 3.7), y = c(0.5, 2.1)) +
  figx.theme -> cp.ln

@@

#cp.grid <- plot_grid(NULL, cp.ln, cp.wei, ncol = 3)

pp.best %>% 
  filter(., dist == "gamma") %>% 
  ggplot(., aes(x = rate, y = shape, color = group)) +
  geom_point(alpha = aval) +
  scale_color_manual(values=colsx, drop=FALSE) +
  lims(x = c(0, 0.23), y = c(0.4, 2.3)) +
  figx.theme -> pp.gam

pp.best %>%
  filter(., dist == "lnorm") %>% 
  ggplot(., aes(x = meanlog, y = sdlog, color = group)) +
  geom_point(alpha = aval) +
  scale_color_manual(values=colsx, drop=FALSE) +
  lims(x = c(0.7, 3.7), y = c(0.5, 2.1)) +
  figx.theme -> pp.ln

pp.best %>%
  filter(., dist == "weibull") %>% 
  ggplot(., aes(x = scale, y = shape, color = group)) +
  geom_point(alpha = aval) +
  scale_color_manual(values=colsx, drop=FALSE) +
  lims(x = c(5, 80), y = c(0, 2.1)) +
  figx.theme -> pp.wei

@@

np.best %>% 
  filter(., dist == "gamma") %>% 
  ggplot(., aes(x = rate, y = shape, color = group, shape = shapeid)) +
  geom_point(alpha = aval) +
  scale_color_manual(values=colsx, drop=FALSE) +
  lims(x = c(0, 0.23), y = c(0.4, 2.3)) +
  figx.theme -> np.gam

np.best %>% 
  filter(., dist == "lnorm") %>% 
  ggplot(., aes(x = meanlog, y = sdlog, color = group, shape = shapeid)) +
  geom_point(alpha = aval) +
  scale_color_manual(values=colsx, drop=FALSE) +
  lims(x = c(0.7, 3.7), y = c(0.5, 2.1)) +
  figx.theme -> np.ln

np.best %>%
  filter(., dist == "weibull") %>% 
  ggplot(., aes(x = scale, y = shape, color = group, shape = shapeid)) +
  geom_point(alpha = aval) +
  scale_color_manual(values=colsx, drop=FALSE) +
  lims(x = c(5, 80), y = c(0, 2.1)) +
  figx.theme -> np.wei

@@

legend.grid <- get_legend(pp.best %>%
  filter(., dist == "lnorm") %>% 
  ggplot(., aes(x = meanlog, y = sdlog, color = group)) +
  geom_point(alpha = aval) +
  scale_color_manual(values=colsx) +
  lims(x = c(0.7, 3.7), y = c(0.5, 2.1)) +
  theme_bw() +
  guides(color = guide_legend(title = "Social Group", ncol = 2,
                              override.aes = list(alpha = 0.9, size = 5))))

cp.grid <- plot_grid(legend.grid, cp.ln, cp.wei, ncol = 3)
